---
title: "R Markdown Demo"
author: "Sarah Wright"
date: "2/4/2021"
output: 
  html_document:
    theme: lumen
params:
  your_email: "sarah_wright@nps.gov"
---
<!--Use include=FALSE to run the code chunk without printing the code or the output (this is a comment and will not show up in the knitted output!)-->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## I am a second-level header
### I am a third-level header

Here is some regular text, **and now it is bold.** *Italics are also an option.* It's easy to type a ^superscript^ or a ~subscript~ too. I can write math equations in $\LaTeX$ in two ways: inline (using single \$), or as *displayed formulas* on their own line (using double \$\$):

$$
A = \pi*r^{2}
$$

-   this
-   is
    -   an
    -   unordered
    -   list

1.  here
1.  is
    a.  an autonumbered
    a.  ordered
    a.  list
    
Here is a [link](https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf?_ga=2.112017668.1404110233.1612472436-803722910.1605737584) to a helpful cheatsheet.

## Showing your work

This is a chunk of R code with the code and the output visible. You can explain what the code does using readable, formatted text, then run the code right here in the same document.
```{r cars}
summary(cars)
```

## Embedding code output

Sometimes you want to show the output of your code (like a plot or a table) without printing the actual code. Use the parameter `echo=FALSE` to do this.
```{r pressure, echo=FALSE}
plot(pressure)
kableExtra::kable(pressure)
```

## Evaluating code inline

This report was generated on `r Sys.Date()`. Please direct any and all complaints to `r params$your_email`.

## Things you can create with R Markdown

-  Notebook (for documenting your work as you write code)
-  Polished html, pdf, or Word reports/articles/etc
    -  Easy to manage citations!
-  Static websites
-  Interactive Shiny documents and dashboards
-  Static html dashboards
-  html slide decks
-  ...and more
